CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-12 codecheck-paper.tex
update limitations

\textbf{Isn't CODECHECK what peer review should be doing already?}
That is correct.  However, the general observation is that the
increasing number of researchers, submissions, and reviews to conduct
under the pressure to publish, puts the scholarly publication system
under a lot of strain.  We also see parallels to the terms
`reproducible research' and `open science'. Establishing a CODECHECK
process is largely an acknowledgement that peer reviewing practices
have faltered to adapt to the challenges of digitisation and
computer-based research or data science. The concept of a CODECHECK,
just as the reproducibility of research and the openness of science,
may be of transitional nature. If the activities described here as
being part of a CODECHECK become the norm for scientific reviews and
publications, then the initiative will have succeeded.  However, the
rapidly changing technology used in research leads us to believe that
a separate role of codechecker and the expertise it brings will be
beneficial in the long term.

@@

% LocalWords:  CODECHECK CODECHECKER Zenodo ORCID ECRs codecheck

>>>>

\textbf{Isn't CODECHECK what peer review should be doing already?}
On the surface, that is correct.
However, the general observation is that the
increasing number of researchers, submissions, and reviews to conduct
under the pressure to publish, puts the scholarly publication system
under a lot of strain.  
Miyakawa described how simply requesting raw data from authors as an 
editor lead to withdrawal or rejection of nearly all submissions where the
request was necessary \cite{miyakawa_no_2020}. Such basic checks that
sufficient data supports the results requires large efforts from editors,
yet they can be based on availability of data files and the content of the
paper. These checks can be enhanced by more complex CODECHECKs asking for
the code, and, because code is not inert but needs to be run in an specific
environment, executing the code.
This might fall within the idealistic expectations for peer review,
but is far from common in reality.
Establishing a CODECHECK
process is largely an acknowledgement that peer reviewing practices
have faltered to adapt to the challenges of digitisation data science.
The concept of a CODECHECK,
just as the reproducibility of research and the openness of science,
may be of transitional nature. If the activities described here as
being part of a CODECHECK become the norm for scientific reviews and
publications, then the initiative will have succeeded.  However, the
rapidly changing technology used in research leads us to believe that
a separate role of codechecker and the expertise it brings will be
beneficial in the long term.

@@

% LocalWords:  CODECHECK CODECHECKER Zenodo ORCID ECRs codecheck codechecker
